---
output: 
  github_document:
    # code_folding: hide
    toc: TRUE

---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Welcome and explanation



<!-- badges: start -->
<!-- badges: end -->

'Do not scatter your energies', 

These days I'm focused a lot on package building.  I need a personal website update update.  Instead of trying to reboot my blogdown website or convert to quarto, I'm just using package building architecture via pkgdown to create an updated personal webpage.  I may explore some meta package writing here as well. 

```{r, echo = F}
library(ggstamp)
packages <- c("ggxmean", "ggstamp", "ggverbatim", "ggcirclepack", "ma206\ndistributions", "ma206\nequations", "ggchalkboard", "ggstates", "tidypivot", "ggsmoothfit", "ggsmoothfit", "doublecrochet", "ggdirect", "ggnc", "ggnorthcarolina" )

ggcanvas() + 
  stamp_polygon(x0y0 = pos_honeycomb(ncol = 5, n = 15), fill = "goldenrod") + 
  stamp_text(xy = pos_honeycomb(ncol = 5, n = length(packages)), label = packages, size = 3)
  
  
```


```


# CV

- [cv](https://github.com/EvaMaeRey/cv/blob/main/reynolds_evangeline_cv.pdf)
- [link to update/suggest an edit](https://github.com/EvaMaeRey/cv/blob/main/reynolds_evangeline_cv.Rnw)

# Bio

Hello and welcome!  I'm a data scientist and educator that's especially passionate about using visualization to facilitate communication and statistical learning.  I'm particularly motivated by the elegance and power of the "Grammar of Graphics" framework, and am exploring how to further empower ggplot2 users to take advantage of the extension space by 1) working on new extension packages for statistical education and 2) providing new points of entry into the ggplot2 world (tutorials/recipes as well as community building).

For the last three years, I've worked in the Dean's Data Cell at the United States Military Academy at West Point in a data analytics and teaching dual role. I worked closely with stakeholders and other members of the data team to deliver actionable insights and meet institutional reporting requirments. I worked on the Deans Data Cell infrastructure towards, code-first, reproducible and elegant data products.  I also taught sections of MA206 Introduction to Statistics and Probability in the Mathematics Department, and oversaw five independent studies focused on tool-building for statistical education.

I have taught statistical methodology  at the University of Denver’s Josef Korbel School of International Studies Visiting Teaching Assistant Professor and have lectured at the Technische Universität Dresden’s Center for International Studies and have consulted on a project with the Violence Prevention Research Program at the University of California Davis. My PhD is from the University of Illinois, where my dissertation won 2018 Burkholder Award for Best Dissertation in the Political Science department of the University of Illinois.

I study effectiveness of international institutions and law especially in the area of security. More broadly, my areas of study have been International Relations, Methodology, and Comparative Politics with an emphasis on Latin American Politics. My dissertation focused on compliance with supranational law, using UN Security Council resolutions as my principle case; I conducted dissertation field research in Brazil in the Federal House of Deputies.

I have extensive experience in data analysis and teaching data science. I worked as a statistics consultant, at the Applied Technologies of the Arts and Science (ATLAS), at the University of Illinois from 2013-2015. I also served “Methods TA” in Political Science in the 2015-2016 academic year at the University of Illinois, providing assistance and expertise both to undergraduate and graduate students. At TU Dresden, in 2018, I designed and taught a course introducing students to data science tools and statistical analysis for political research. I primarily teach methodology and data science courses at the Korbel School. Research interests in methodology include communicating uncertainty, visual exposition of statistical concepts and electoral rules.

I have been awarded the Fulbright Fellowship (Argentina 2008), Foreign Language and Area Studies Fellowships (2009-2011), Nelle Signor Travel Fellowship (Brazil 2011) and have participated in specialized workshops including the Empirical Implications of Theoretical Models (2010), Public Policy and Nuclear Threats (2013), the Berkeley Institute for Transparency in the Social Sciences (2015) workshops, the Zurich Summer School for Women in Political Methodology (2017), and the Lorentz Workshop: Empirical Research on International Organizations (2018).

Previously to my academic career, I worked at the U.S. Department of Commerce’s Bureau of Industry and Security in chemical and biological export controls and have worked in lithium-ion battery failure diagnostics at the Chemical Engineering Division of Argonne National Laboratory.


# Recent Talks
 
- [Speaking ggplot2, April 2022, West Point Data Analytics Series](https://evamaerey.github.io/mytidytuesday/2022-04-21-ggplot2-grammar-primer/ggplot2_grammar_primer.html#1)
- [Creating new geom_*s for richer statistical storytelling, May 2022, West Point Department of Mathematics Talk Series](https://evamaerey.github.io/mytidytuesday/2022-05-09-statistical-geometries/statistical_geometries.html#2)
- [Flipbooks, January 2020, RStudio Conference](https://youtu.be/9Sgg1lJRM8c?si=Q28CtH59Df8DRmbI&t=408)
- [tidypivot]()
- [Extending ggplot2 statistical geometries, MAA Metro New York May 2021](https://evamaerey.github.io/ggxmean/talk_maa_metro_ny.html#1)
- [Intro to Network Analysis and Visualization](https://evamaerey.github.io/mytidytuesday/2022-05-23-networks-presentation/networks_presentation.html#1)
- [Shallow Fakes: Assessing the potential for spoofing and faking in data visualization and what to do about it, University of Denver May 2019]()



# Projects and Goals

- ggplot2 flipbook
- a ggplot2 grammar guide
- easy geom recipes: diving into defining compute_group ggprotos
- more geom recipes: cases when compute_group is not enough (compute_panel)
- ggtedius workshop
- ma206verse/stats101verse
- ggnc, ggnorthcarolina, ggbrazil, and beyond: geographic location names as positional aesthetics

# What I'm working on: my packages and repos

```{r}


```

ggtedious a demo package for messages, warnings, errors and test in ggplot2 extension "Testing your code can be painful and tedious, but it greatly increases the quality of your code."

ggsmoothfit extending stat_smooth to return fitted values and residuals  R  1 Updated last week
more_theme_easing_ideas R Updated last week

ggols
visual expositions of simpler linear models
 CSS  6  1 Other Updated 2 weeks ago
ggverbatim
tabular data to tabular viz
 R  2 Updated 3 weeks ago

readme2pkg
collection of functions to write packages and promo mostly from within README.Rmd
 R Updated 3 weeks ago

ggjudge
Say what you think about a plot up front
 R Updated 3 weeks ago

flipbookr
Presenting code step-by-step and side-by-side with its output
 R  191  19 Other Updated 3 weeks ago

ggwipe
remove stat and geom layers from plot; return the last plot but wiped
Updated last month

gglobalclocks
global clocks!
 1 Updated on Jul 23

ggnorthcarolina
 R  3 Updated on Jul 20

tidybernoulli
probability branching in data frames
matrix
probability
tidy-data

ggnc
North Carolina specific geoms experiment
 HTML Updated on Jun 27
easy-geom-recipes


tidypivot
Declarative group-wise count and compute, describing your target table
 R  8 Other Updated on Jun 22
 

ggdistricts
 R Updated on Jun 15

ggstates
 R Updated on Jun 12

ggbody
using ggplot2 w/ body atlases
 R  1 Updated on May 30

ma206distributions
data-science
ggplot2
statistics
data-analysis
 R  2 Other Updated on May 1

ggfips
A new approach to ggplot spatial APIs as demonstrated with with county fips codes
 R  1 Updated on Apr 26

everyday_ggplot2_extension
a practical approach to ggplot2 extension
 4 Updated on Apr 26
 
tidytitanic 
flat versions of the r titanic data
 R  1 Other Updated on Apr 17

ggbrazil 
Updated on Apr 17

ggcirclepack 
Experimental; write up for ggplot2 extenders meet up
 R  4 Updated on Apr 14
ma206equations 
Make writing equations easy in markdown and plots
 R Other Updated on Apr 10

codequote4shiny 
Return R code that will produce plot/df/text in a shiny app. For package demos and teaching purposes
 1 Updated on Mar 9

ggchalkboard 
 R  2 Updated on Nov 26, 2022
 

ggxmean 
 R  60  3 MIT License Updated on Oct 11, 2022

tidytuesday_colorswatches 
leaf through tidytuesday datasets
 HTML  1 Updated on Oct 5, 2022


ggsample 
spin off of ggxmean, educational, random sampling, bootstrapping etc
 R  1 Other Updated on Aug 19, 2022

tabylextra 
For flattening, lengthening janitor tabyls
 R  1 Updated on Jul 7, 2022
 
ggstamp 
stamp_* as an API for annotation layers
 R  37 Updated on Jun 27, 2022

ma206datapackageresourses Private
Share and prepare to build ma206data package
Updated on Apr 27, 2022
ggpivot 

ggpivot 

ggquiet 
 R  1 Other Updated on Jan 17, 2022
codeexplode 
explodes code
 CSS  2 Other Updated on Jan 17, 2022

doublecrochet 
Show .Rmd source paired with output!
 JavaScript  8 Other Updated on Jan 8, 2022
 

ggextend 
a toy package with examples of ggplot extension functions
 R  1 Updated on Oct 25, 2021

ay_2022_2_advanced_individual_study- 
Here, laying out some objectives for independent study, MA489!
 HTML  1 Updated on Oct 12, 2021

ggmemory 
parsing and presenting viz and manipulation code pipeline history using xaringan and flipbookr
 CSS  1 Other Updated on Oct 9, 2021





exampleexploder 
explodes examples
 R Other Updated on Aug 20, 2021
 
codehover 
Forked from arthurwelle/codehover
Hoverable HTML Table for Displaying Intermediary Code Results (e.g. Pipes)
 R Updated on Aug 16, 2021


ggdirect 
Some functions that do more calculation in the background to get you there faster -- especially focusing on direct labeling.
 R  1 Updated on Aug 14, 2021


xaringanPrinter 
convert xaringan/remark.js slides to Xaringan
 R  7  1 Other Updated on Jun 22, 2021
xaringanBuilder 
Forked from jhelvy/renderthis
An R package for building xaringan slides into multiple outputs, including html, pdf, png, gif, pptx, and mp4.
 R Other Updated on Jun 20, 2021


madlibs 
For replacing words with blanks, or partial replacement of word with blanks
 CSS  1 Other Updated on May 8, 2021
package_templates_plus 
Where do the rendered package templates get to live or key package examples? Right here.
 HTML Updated on Apr 14, 2021

teaching_spring_2021 
Some stuff for the students
 HTML Updated on Mar 17, 2021
education.rstudio.com 

ma206_tidyverse_code_movies 
 HTML  2 Updated on Jan 16, 2021


# unblogs: experiments and code demos

- mytidytuesday
- featurette
- ggpuzzles minimal not-working examples
- hexes Creating some hex stickers for packages

